---
title: "How can I use R to get my work done?"
subtitle: "Lets examine a few use cases..."
author: "John Minter"
date: "2018-07-13"
output:
  xaringan::moon_reader:
    css: ["./css/jrm-theme.css"]
    lib_dir: libs
    nature:
      ratio: "16:9"
      highlightStyle: github
      highlightLines: true 
      countIncrementalSlides: false
---
```{r setup, include=FALSE}
options(htmltools.dir.version = FALSE)
```

# Chris Wiggins: Statistics education is changing...

--

1. Technology is disrupting how we do things at an increasing rate.

--
  - Anything important that can be automated will be automated.

--

  - Anything that is purely procedural can be automated.
  
--

2. So what should we most want for our students?

--

  - The ability to do things machines can’t do!

---

# Chris Wiggins: Minimizing Cognitive Demands

1. The average person can only hold two to six pieces of information in their attention at once!

   - Source: Cowan, 2000

--

   - Moral: Short‐term memory is a scarce resource.    
     <span style="color:#99ccff"> Spend it wisely </span>!

---

# Chris Wiggins: Main strategy

1. First establish big picture visions and their value

  - Aim for retention of
    <span style="color:#99ccff">what matters most</span>...
  - > ...and the vision that was planted in my brain still remains...    
    Paul Simon, "The Sound of Silence"
--

2. Then backfill details later <span style="color:#99ccff">
    as the opportunity arises</span>.

---

# Use R to summarize data

```{r cars, comment=NA}
summary(cars)
```

---

# Use R base graphics to include plots

```{r pressure, fig.width= 11.0, fig.height=5.0, echo=FALSE, fig.align='center'}
plot(pressure)
```

Note that the `echo = FALSE` parameter was added to the code chunk
to prevent printing of the R code that generated the plot.

---

# Use R to analyze a distribution of weights

Make a dataframe with data simulating a population of 200 males and 200 females

```{r make distribution, comment=NA}
set.seed(42)
df <- data.frame(gender = factor(rep(c("F", "M"), each = 200)),
                 weight = round(c(rnorm(200, mean = 55, sd=5),
                                  rnorm(200, mean = 65, sd=5))))

summary(df)
```

---

# Use ggplot2 to plot the results

```{r endWithANull, echo=FALSE, fig.height=6.0, fig.width=14.5}
library(ggplot2)
txtSize <- 16
plt <- ggplot(df, aes(x=weight, fill=gender)) +
       geom_density(alpha=0.5) +
       geom_hline(yintercept = 0, colour='white') +
       # ggtitle("Weight as a function of gender") +
       theme(axis.text=element_text(size=txtSize),
             axis.title=element_text(size=txtSize),
             legend.title=element_text(size=txtSize),
             legend.text=element_text(size=txtSize),
             plot.title=element_text(hjust = 0.5)) +
       # geom_histogram() +
       NULL
print(plt)
```

---

# .blue[Thank you!]

.font200[.blue[Contact me...]]

.font150[.yellow[`r anicon::faa("twitter", animate="float")` @jrminter ]]

.font150[.yellow[`r anicon::faa("envelope", animate="float")` jrminter@gmail.com ]]

.font150[.yellow[`r anicon::faa("github", animate="float")` code available at github ]].font150[(.blue[https://github.com/jrminter])]





