---
title: "Notes on css etc from apreshill ohsu"
author: "John  Minter"
date: "2018-07-08"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Questions from `ohsu-fonts.css`

**eot**: The Embedded OpenType format, which enables designers to
specify EOT fonts for use on defined Web pages, was developed by
Microsoft and made available as part of the Internet Explorer([R])
browser. [source](https://acronyms.thefreedictionary.com/EOT).

**woff2**: Google Chrome Developers says:

> The new WOFF 2.0 Web Font compression format offers a 30% average gain
> over WOFF 1.0 (up to 50%+ in some cases). WOFF 2.0 is available since
> Chrome 36 and Opera 23. [source](https://gist.github.com/sergejmueller/cf6b4f2133bcb3e2f64a)

# Colors from `ohsu.css`

```{r, echo=FALSE, fig.cap="Color descriptions"}
library(pander)
df <- read.csv('./dat/colors.csv',  header=TRUE, sep=",")
panderOptions("table.split.table", Inf)
panderOptions("table.alignment.rownames", "left")
panderOptions("table.alignment.default", "left")

pander(df)

```

