---
title: "A Simple Example"
subtitle: "A basic modification of Emi Tanaka example"
author: "John Minter"
date: "June 29, 2018"
output:
  xaringan::moon_reader:
    css: [./css/tanaka.css]
    lib_dir: libs
    seal: false 
    self_contained: false
    nature:
      ratio: "16:9"
      #autoplay: 30000 #countdown: 
      highlightStyle: github
      highlightLines: true
      countIncrementalSlides: false
---

```{r setup, include=FALSE}
options(htmltools.dir.version = FALSE)
```


class: title-slide

<br><br>
# A Simple Example

### **John Minter**

### June 28, 2018

<br>

[.textshadow[.font120[`r anicon::faa("twitter", animate="float", color="white", rtext=".white[@jrminter]")`]]](http://twitter.com/jrminter)

<br><br><br>
---

class: center, middle


```{r cars}
summary(cars)
```

---

class: center, middle

## Including Plots

You can also embed plots, for example:

```{r pressure, echo=FALSE}
plot(pressure)
```

Note that the `echo = FALSE` parameter was added to the code chunk
to prevent printing of the R code that generated the plot.

---
class: center, middle

### The distribution of weights from a simulated population

```{r endWithANull, echo=FALSE, fig.height=6.5, fig.width=14.5}
library(ggplot2)
set.seed(42)
df <- data.frame(gender = factor(rep(c("F", "M"), each = 200)),
                 weight = round(c(rnorm(200, mean = 55, sd=5),
                                  rnorm(200, mean = 65, sd=5))))
txtSize <- 16
plt <- ggplot(df, aes(x=weight, fill=gender)) +
       geom_density(alpha=0.5) +
       geom_hline(yintercept = 0, colour='white') +
       # ggtitle("Weight as a function of gender") +
       theme(axis.text=element_text(size=txtSize),
             axis.title=element_text(size=txtSize),
             legend.title=element_text(size=txtSize),
             legend.text=element_text(size=txtSize),
             plot.title=element_text(hjust = 0.5)) +
       # geom_histogram() +
       NULL
print(plt)
```

---

class: title-slide

<br><br><br><br>

# .textshadow[.font150[Thank you!]]
<br><br><br>


## .textshadow[**John Minter**]

[.textshadow[.font150[.white[`r anicon::faa("twitter", animate="float")` @jrminter]]]](http://twitter.com/jrminter)

.textshadow[.font150[.white[`r anicon::faa("envelope", animate="shake", anitype="parent-hover", rtext="jrminter@gmail.com")`]]]


[.textshadow[.font150[`r anicon::faa("github", animate="ring", anitype="parent-hover", color="white", rtext=".white[code available at github]")`]]](https://github.com/jrminter)


