---
title: "Preparing LCS Statistics Students for the future"
subtitle: "Developing critical thinking & and analysis skills"
author: "John Minter"
date: "2018-07-14"
output:
  xaringan::moon_reader:
    css: ["./css/lcs-theme.css"]
    lib_dir: libs
    nature:
      ratio: "16:9"
      highlightStyle: github
      highlightLines: true 
      countIncrementalSlides: false
---
```{r setup, include=FALSE}
options(htmltools.dir.version = FALSE)
```

# Statistics education is changing...

--

1. Technology is .blue[disrupting] how we do things at an    
   .blue[increasing rate].

   - Anything important that can be automated .yellow[will be automated].

   - Anything that is purely procedural .yellow[can be automated].

--

2. So what should we .blue[want most] for our students?

   - The .yellow[ability to do things machines can’t do]!

.font130[Source: .blue[Chris Wiggins], Prof. of Statistics, Univ of. Auckland (July 2018)]
---

# Chris Wiggins: Minimizing Cognitive Demands

1. The average person can only hold .blue[two to six]
   pieces of information in their attention at once!

   - Source: N. Cowan, *Behavioral and Brain Sciences*, **24**, 87-185, (2000).

--

   - Moral: Short‐term memory is a scarce resource.    
     <span style="color:#99ccff"> Spend it wisely </span>!

---

# Chris Wiggins: Main strategy

1. First establish big picture visions and their value

  - <span style="color:#99ccff">Long-term retention</span>
    from college statistics courses has
    been <span style="color:#99ccff">poor</span>.

  - Aim for retention of
    <span style="color:#cccc00">what matters most</span>...
--

2.  Backfill details later <span style="color:#99ccff">
    as the opportunity arises</span>.

---

# Countermeasures

1.  Use relevant data sets to encourage exploration,
    critical analysis, and communicating understanding.

2.  Use modern Open Source software that students are
    likely to use in college and in their jobs.

3.  Use reproducible workflows that encourage sharing
    and reduce errors.

---

# Use R to summarize data

```{r cars, comment=NA}
summary(cars)
```

---

# Use R base graphics to include plots

```{r pressure, fig.width= 11.0, fig.height=5.0, echo=FALSE, fig.align='center'}
plot(pressure)
```

.font120[Note that the `echo = FALSE` parameter was added to the code chunk
to prevent printing of the R code that generated the plot.]

---

# Use R to analyze a distribution of weights

.font120[Make a dataframe with data simulating a population of 200 males and 200 females]

```{r make distribution, comment=NA}
set.seed(42)
df <- data.frame(gender = factor(rep(c("F", "M"), each = 200)),
                 weight = round(c(rnorm(200, mean = 55, sd=5),
                                  rnorm(200, mean = 65, sd=5))))

summary(df)
```

---

# Use ggplot2 to plot the results

```{r endWithANull, echo=FALSE, fig.height=6.0, fig.width=14.5}
library(ggplot2)
txtSize <- 16
plt <- ggplot(df, aes(x=weight, fill=gender)) +
       geom_density(alpha=0.5) +
       geom_hline(yintercept = 0, colour='white') +
       # ggtitle("Weight as a function of gender") +
       theme(axis.text=element_text(size=txtSize),
             axis.title=element_text(size=txtSize),
             legend.title=element_text(size=txtSize),
             legend.text=element_text(size=txtSize),
             plot.title=element_text(hjust = 0.5)) +
       # geom_histogram() +
       NULL
print(plt)
```

---

# An example from Yihui Xie

.pull-left[
- a bullet
- another bullet
]

.pull-right[
- a bullet
- another bullet
]

---

# Quotes

.pull-left[.font150[
> Not having all of the bells and whistles that Keynote and PowerPoint do **forces you to present your work simply**, and I think that when you do this properly, **it is very powerful**.    
-- Nick Tierney]
]

.pull-right[.font150[
> **Less is more**.    
-- Yihui Xie]
]

---

# .blue[Thank you!]

.font200[.blue[Contact me...]]

.font150[.yellow[`r anicon::faa("twitter", animate="float")` @jrminter ]]

.font150[.yellow[`r anicon::faa("envelope", animate="float")` jrminter@gmail.com ]]

.font150[.yellow[`r anicon::faa("github", animate="float")` code available at github ]].font150[(.blue[https://github.com/jrminter])]





