---
title: "How can I use R to get my work done?"
subtitle: "Lets examine a few use cases..."
author: "John Minter"
date: "2018-07-04"
output:
  xaringan::moon_reader:
    css: ["default","./css/jrm-fira-sans.css"]
    lib_dir: libs
    nature:
      ratio: "16:9"
      highlightStyle: github
      highlightLines: true 
      countIncrementalSlides: false
---
```{r setup, include=FALSE}
options(htmltools.dir.version = FALSE)
```

<div class="my-logo-left"></div>

# Use R to summarize data

```{r cars}
summary(cars)
```

---

<div class="my-logo-left"></div>

# Use R to include plots

```{r pressure, fig.width= 11.0, fig.height=5.0, echo=FALSE, fig.align='center'}
plot(pressure)
```

Note that the `echo = FALSE` parameter was added to the code chunk
to prevent printing of the R code that generated the plot.

---

<div class="my-logo-left"></div>

# Use R to analyze a distribution of weights

Make a dataframe with data simulating a population of 200 males and 200 females

```{r make distribution, comment=NA}
set.seed(42)
df <- data.frame(gender = factor(rep(c("F", "M"), each = 200)),
                 weight = round(c(rnorm(200, mean = 55, sd=5),
                                  rnorm(200, mean = 65, sd=5))))

summary(df)
```

---

<div class="my-logo-left"></div>

# Use R to plot the results

```{r endWithANull, echo=FALSE, fig.height=6.0, fig.width=14.5}
library(ggplot2)
txtSize <- 16
plt <- ggplot(df, aes(x=weight, fill=gender)) +
       geom_density(alpha=0.5) +
       geom_hline(yintercept = 0, colour='white') +
       # ggtitle("Weight as a function of gender") +
       theme(axis.text=element_text(size=txtSize),
             axis.title=element_text(size=txtSize),
             legend.title=element_text(size=txtSize),
             legend.text=element_text(size=txtSize),
             plot.title=element_text(hjust = 0.5)) +
       # geom_histogram() +
       NULL
print(plt)
```

---

<div class="my-logo-left"></div>

# .font120[Thank you!]

## **John Minter**

.font200[.blue[`r anicon::faa("twitter", animate="float")` @jrminter ]].font200[ (http://twitter.com/jrminter)]

.font200[.blue[`r anicon::faa("envelope", animate="float")` jrminter@gmail.com ](].font200[.red[ jrminter@gmail.com])]

.font200[.blue[`r anicon::faa("github", animate="float")` code available at github ]].font200[(.red[https://github.com/jrminter])]
